### 2015-12-20 outline.tex
expand section on cross-industry variation

\vskip.3in
Main idea: adapt SOP model to predict whether anti-dumping measures get renewed
\begin{itemize}
	\item Note that this is not trade war: foreign is applying $\tau^{*a}$ in most / all cases
		\begin{itemize}
			\item \textbf{Q}: Are all cases of renewal ones of no punishment, i.e. target country is applying MFN tariff?
		\end{itemize}
	\item When is it worth it for lobby to exert effort to renew AD measure?
	\item Lobby must be able to trigger the AD measure in the first place
		\begin{itemize}
			\item This means disputes/non-adherence to MFN tariffs must happen on the equilibrium path
			\item Need uncertainty, asymmetric information, something
			\item In my model, it is symmetric political uncertainty about how legislators (modeled in reduced form as position of median legislator) will vote
		\end{itemize}
	\item In this setup, need ``dispute'' to last for 5 periods (years)
		\begin{itemize}
			\item Then can extend it.
			\item \textbf{Q}: for five more years?
		\end{itemize}
	\item Why would there be variation in one lobby's incentives between $t=1$ (original application of AD) and $t=6$ when it comes up for renewal?
		\begin{itemize}
			\item Uncertainty could be an answer, \textit{and} it varies across industry
			\item \textbf{Q}: Is this a plausible story?
		\end{itemize}
	\item Also have to adapt model to cross-industry to get necessary variation
		\begin{itemize}
			\item I've already done some of this leg-work for the NSF proposals, thinking about PTA project
		\end{itemize}
\end{itemize}

\vskip.5in
Possible cross-industry variation
\begin{itemize}
	\item Industry / lobby gets richer / more insulated for five years
		\begin{itemize}
			\item This could lead to differences in budget constraint if that were in model
			\item This could lead to differences in ability to deal with technological gap with foreign competitors 
				\begin{itemize}
					\item \textbf{Q}: This is one of the arguments for escape clause, no?
				\end{itemize}
		\end{itemize}
	\item Lobby facing same uncertainty, behaving in same manner may get different outcome in the two draws (five years apart)
	\item Uncertainty could change, so behavior would change (this would be hard to pick up in the data that I have)
\end{itemize}

>>>>

\vskip.3in
Main idea: adapt SOP model to predict whether anti-dumping measures get renewed
\begin{itemize}
	\item Note that this is not trade war: foreign is applying $\tau^{*a}$ in most / all cases
		\begin{itemize}
			\item \textbf{Q}: Are all cases of renewal ones of no punishment, i.e. target country is applying MFN tariff?
		\end{itemize}
	\item When is it worth it for lobby to exert effort to renew AD measure?
	\item Lobby must be able to trigger the AD measure in the first place
		\begin{itemize}
			\item This means disputes/non-adherence to MFN tariffs must happen on the equilibrium path
			\item Need uncertainty, asymmetric information, something
			\item In my model, it is symmetric political uncertainty about how legislators (modeled in reduced form as position of median legislator) will vote
		\end{itemize}
	\item In this setup, need ``dispute'' to last for 5 periods (years)
		\begin{itemize}
			\item Then can extend it.
			\item \textbf{Q}: for five more years?
		\end{itemize}
	\item Why would there be variation in one lobby's incentives between $t=1$ (original application of AD) and $t=6$ when it comes up for renewal?
		\begin{itemize}
			\item Uncertainty could be an answer, \textit{and} it varies across industry
			\item \textbf{Q}: Is this a plausible story?
		\end{itemize}
	\item Also have to adapt model to cross-industry to get necessary variation
		\begin{itemize}
			\item I've already done some of this leg work for the NSF proposals, thinking about PTA project
		\end{itemize}
\end{itemize}

\vskip.5in
Possible cross-industry variation
\begin{itemize}
	\item Lobby facing same uncertainty, behaving in same manner may get different outcome in the two draws (five years apart)
	\item Industry / lobby gets richer / more insulated for five years
		\begin{itemize}
			\item This could lead to differences in budget constraint if that were in model
			\item May not need budget constraint if extra budget allows them to invest in technology
				\begin{itemize}
					\item Come to question of whether protection and technological upgrading are complements or substitutes
					\item Lobbies that have more to gain have more opportunity to \textit{either} gather strength to become more competitive \textit{or} become more politically powerful to seek more protection
					\item Perhaps some cross-industry measure of restraints on political strategy that would push toward substituting to technological
				\end{itemize}
			\item This could lead to differences in ability to deal with technological gap with foreign competitors 
				\begin{itemize}
					\item \textbf{Q}: This is one of the arguments for escape clause, no?
				\end{itemize}
		\end{itemize}
	\item Uncertainty could change, so behavior would change (this would be hard to pick up in the data that I have)
\end{itemize}
